NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-02-08 Manuscript/manuscriptPS.tex
Update manuscriptPS.tex

\emph{Numerical simulations of S-DROSS curves.}
The numerical simulations of S-DROSS curves were performed with the SIMPSON simulation package \cite{bak00}
using as input the $^{13}$C--$^1$H
dipolar couplings, either as determined by the R-PDLF experiments, or as calculated from the known $^2$H quadrupolar couplings \cite{browning80}.
The chemical shift anisotropy and homonuclear couplings were neglected, and the input file {\it{rep2000}} was used to simulate a random
distribution of bilayer orientations in the samples studied.

>>>>

\emph{Numerical simulations of S-DROSS curves.}
The numerical simulations of S-DROSS curves were performed with the SIMPSON simulation package \cite{bak00}
using as input the $^{13}$C--$^1$H
dipolar couplings, either as determined by the R-PDLF experiments, or as calculated from the known $^2$H quadrupolar couplings \cite{browning80}.
The chemical shift anisotropy and homonuclear couplings were neglected, and the input file {\it{rep2000}}\todo{citation needed?} was used to simulate a random
distribution of bilayer orientations in the samples studied.
